### 2022-10-21 doc/PRF2022/Reviews/ResponseToReviewer2.tex

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Cecile Cottin-Bizonne,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1 and 2 are colored in \textcolor{red}{red} and 
\textcolor{magenta}{magenta}, respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei Fu, Rolf Ryham, Bryan Quaife, and Yuan-Nan Young

\section*{Response to Reviewer 2}
\comment{
\noindent
I report here on the manuscript "Effects of tunable hydrophobicity on the
collective hydrodynamics of Janus particles under flows" by Szu-Pei Fu et al.
submitted for publication to Physical Review Fluids. The authors have conducted
numerical hydrodynamic simulations in 2D on the self-assembly and dynamics of
nanoscale Janus particles under simple shear flow and Taylor-Green flow using
the method of discretized boundary integrals to describe the motion of the
particles immersed in 2D Stokes flow. The Janus character of the individual
particles is realized by tuning the local hydrophobicity/hydrophilicity. The
authors have previously shown that this system forms vesicle-like structures and
investigated such structures in simple shear flow (reference [18] in the paper).
The authors now continue this work by studying different model systems by tuning
the local hydrophobicity to model (i) bilayer-forming amphiphilic particles,
(ii) formation of multilamella structures, and (iii) formation of block-chain
structures, all pre-assembled under quiescent flow conditions. These equilibrium
structures are then studied under flow of varying shear rate. The different
structures are characterized by (i) a deformation order parameter, (ii) an
orientation order parameter, and (iii) the free energy. The authors study the
dynamics of the structures under flow, when mapping to physical scales, on the
order of micro-seconds, for nanometer-sized particles and shear rates on the
order of smaller than nanoseconds$^{-1}$. The effect of shear on the conformations
is analyzed in detail, and the results are discussed with respect to related
previous literature.\\ \\
In principle I think the paper meets the criteria to be considered as an article
for Physical Review Fluids in terms of originality, quality, and presentation.
However, I am not yet convinced about the potential applicability to real
systems, as raised below:}

\begin{itemize}
  \item {\bf Response to Summary}: We thank the Reviewer for this positive appraisal of 
our manuscript. 
\end{itemize}

%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}

\noindent
\comment{1) The authors study the nano-hydrodynamics around the JPs very carefully by
modeling the flow as a continuous 2D Stokes flow. While I understand that
modeling the dynamics in 2D instead of 3D is fair, i.e. their results should in
principle be extensible to 3D, my major concern is the absence of thermal
fluctuations. They are expected to be very relevant on the nanometer scale,
regarding self-assembly, dynamics and stability of the JP structures.
}

\begin{itemize}
  \item Response:

  \item Change:

\end{itemize}

\noindent
\comment{2) The shear rates studied are below nanoseconds$^{-1}$. What is the relevance of
such small shear rates in real (biological) systems? Furthermore, in presence of
noise, I would expect that the JP diffusive timescale is much smaller then the
shear flow time scale, and hence effectively the associated Peclet number, i.e.
importance of flow compared to noise, is negligible in this system?}

\begin{itemize}
  \item Response:

  \item Change:

\end{itemize}

\noindent
\comment{Before I can recommend publication, the authors should clarify these points, in
particular justify why noise can be neglected, and why such small shear rates
are relevant.}

\begin{itemize}
  \item Response: 
\end{itemize}

\end{document}

### 2022-11-01 NSF2022/Description/background.tex
pushed organizational changes

@@

\section{Background}
\label{sec:background}
%The goal of this collaborative proposal is to use mathematical modeling
%and numerical simulations to investigate the dynamic self-assembly of
%amphiphilic particles interacting via hydrophobic forces in solvent.
This collaborative proposal aims to advance
the mathematical modeling and numerical simulation
of dynamic self-assembly of amphiphilic particles interacting
via hydrophobic forces in solvent.
Amphiphilic particles such as lipid molecules possess both hydrophobic
and hydrophilic structures. In a viscous solvent they self-assemble into
meso-/macroscopic structures such as micelles and bilayers of lipids to
shield their hydrophobic surfaces from contact with the solvent
molecules e.g., waters. Such self-assembly of amphiphiles via hydrophobic
forces is ubiquitous in biology~\cite{Israelachvili1954},
and has been a major source of nonspecific interactions 
in soft matter~\cite{Sanchez-IglesiasEtAl2012_ACSNano,
AltantzisEtAl2013_PSC, XieYangLuEtAl2020_COCIS}. 
%The proposed research aims to provide fundamental understanding of the
%self-assembly dynamics of amphiphilic particles so to design smart
%materials of desirable properties by
%tuning the geometry and properties of the amphiphilic particles.

%The hydrophobic force arises when polar solvent molecules come in
%contact with a non-polar substance, such as hydrocarbon or vapor.
%In a polar solvent (like water), the dipole-dipole interaction between
%solvent molecules form a loosely structured hydrogen-bond network where
%each solvent molecule shares bonds with neighboring molecules at any
%given time \cite{Israelachvili1954}. In the presence of a non-polar
%solvent molecule loses the ability to form hydrogen bonds
%in one direction. 
%The decrease in the number of hydrogen bonds causes a reorientation,
%or structural change, in the surrounding water that is energetically
%very unfavorable \cite{Bjorneholm2016}.

\begin{wrapfigure}[15]{r}{0.37\textwidth}
\vspace{-8pt}
\centerline
{
\includegraphics[width=0.36\textwidth]{figures/LongRangeForce.jpg}
}
%\vspace{-20pt}
\caption{\label{fig:force_distance}
Force-distance curve for surfactant
monolayers adsorbed on mica reveals a long-range
attraction~\cite{Lin2005}.}
\end{wrapfigure}

Macroscopically, the substantial free energy of placing hydrophobic
surfaces in contact with water is roughly proportional to the surface
area of the contact region~\cite{Bjorneholm2016}.
%As a result, hydrocarbon solutes have a large interfacial tension 
%and try to minimize their surface area when in water. 
At the microscopic level, however, there is long-range interaction
between hydrophobic surfaces. Two hydrophobic surfaces, in particular,
separated by water over some distance, experience an attraction
called the
hydrophobic force~\cite{Lum1999, Meyer2006, Hammer2010, KaScScNe16}.
The force is nonadditive~\cite{SilveraBatista1242477},
and measurements show that the hydrophobic force decays exponentially with a
decay length on the order of 1--10 nm~
\cite{Israelachvili1984,Marcelja1977,Christenson2001,Lin2005,Taetal13}
(Figure \ref{fig:force_distance}).

Motivated by its broad applicability to biology, chemistry, and engineering,
PIs RR and YNY developed a mathematical model, called the
hydrophobic attraction potential (HAP) model~\cite{Fu2018_SIAM},
that is based on
the linear response of water to surface perturbations. This model was
used by all the PIs to show how amphiphilic Janus particles (JP)
self-assemble into a vesicle-like structure~\cite{FuQuRyYo22}.
Janus particles are typically spherical particles with a biphasic
material label on either hemisphere \cite{CaFaRaVe89,Gaetal13,Mallory2017,HaBr20,McBr21}.
Based on
preliminary results (\S\ref{sec:preliminary_work}), the PIs propose to
extend this HAP model as a general methodology that leads
to new mathematical ideas and efficient numerical methods.

\subsection{Hydrophobic attraction}
The hydrophobic attraction potential theory concerns the self-organization of
hydrophobic particles in a viscous solvent. It is a phenomenological
model mimicking the linear-response of water to surface perturbations
and stems from work of Stjepan Mar\v{c}elja
from the Australian National University in 1976. To explain certain
repulsion measurements between lecithin bilayers, Mar\v{c}elja and
coworkers devised a mathematical model using a Landau expansion of the
free energy density of an order parameter for the orientation of
water~\cite{LeRaPa77, MaRa76, LANDAULIFSHITZ5}. Their truncated free
energy gave a boundary value problem for water structure that was
readily solved in terms of hyperbolic trigonometric functions.

Although schematic, the model was general enough to explain a number of
physical effects. For example, the repulsion of lecithin bilayers
was explained by the free energy that decreases with distance of
separation because of the mean orientations of water being opposite at
the two interfaces. Later, a long-range attractive force between
hydrocarbon coated mica sheets was measured up to
100~nm~\cite{ClCh88,RaDe88}. The Mar\v{c}elja
theory was then applied to this problem for an order parameter
representing the excess number of hydrogen bonds per water
molecule and gave agreement with the measured force
curves~\cite{ErLjCl89}.

Analogues of Mar\v{c}elja's phenomenological theory appeared in other
areas related to biological self-assembly, such as interactions of
membrane-bound proteins~\cite{KoNa15, Nagle17, KUZMIN2005} and the
theory of polymer bead interaction in mixed solvents~\cite{deGe76}. On
the downside, it applies a continuum theory to distances of a few
molecular diameters, the association of order parameter is arbitrary, it
predicts monotonic forces, and finally the theory does not account for
the amplification in attraction at very short distances~\cite{Ni80}.

\begin{wrapfigure}[21]{l}{0.3\textwidth}
  \vspace{-5pt}
\includegraphics[width=0.3\textwidth]{figures/Fissure.jpg}
\includegraphics[width=0.3\textwidth]{figures/Landscape.jpg}
\caption{\label{fig:fissure} In fusion, fissures in the phospholipid
  monolayers expose hydrocarbon to water (top). The energy of fissures
  dominates first and third stages of fusion (bottom).
}
\end{wrapfigure}
Despite the ubiquity of
the phenomenon, theoretical developments explaining the basic underlying
principles of the hydrophobic effect have come relatively
late~\cite{Ch05}.
No single theory has been able to account, either qualitatively
or quantitatively,
for hydrophobic interaction over the full distance
regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
For example, studies of the partitioning of
hydrophobic solutes provide estimates for the energy cost of creating
hydrophobic-water contacts
that is a factor of three lower than the value derived from interfacial
tension measurements. Only recently was an explanation for this
discrepancy provided~\cite{Jackson2016}.

The continuum approach to water structure
that we present here is justified
\textit{a posteriori} by the agreement between theory and experiment.
Researchers have used Mar\v{c}elja's theory to calculate
energies of pore formation and fusion~\cite{Gletal88, Aketal17,
RyKlYaCo16}.
%When open, the attraction between apposing hydrophobic
%surfaces causes the fissure to collapse.
PI RR calculated a least energy path 
of fusion using a modified form of the Helfrich energy that
included Mar\v{c}elja's free energy for the structure of water
separating fissures~\cite{RyKlYaCo16} (Figure~\ref{fig:fissure}).
The calculated barrier heights were 
corroborated experimentally \cite{FrRoPi17}. In summary,
there is a consensus that despite its apparent simplicity, the predictions
of the hydrophobic attraction potential theory are compatible with
experimental measurements and may closely mirror the reality of
the physical process at a molecular scale~\cite{FrRoPi17, Fretal21}.

The HAP is a conceptual advance for modeling bilayer membranes.
Continuum elastic energies of membrane assume an energy density that
depends quadratically on the bilayer strain
\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The coefficients
of the continuum ansatz correspond to experimentally measured elastic
moduli \cite{Nagle17, Nagle17-2, NAGLE2000159}.  The HAP approach can
potentially explain membrane properties from first principles because it
derives elastic energies assuming parameters for the water structure and
particle shape \cite{Fu2018_SIAM, FuQuRyYo22, doi:10.1063/5.0009734,
LiAn-Chang16}.  Immersed boundary and boundary integral are highly
effective for modeling intact, giant unilamellar vesicles (GUV) because
they use relatively large time-step sizes and mesh sizes
\cite{
Shravan09,
Rahimian15,
KimLai2010_JCP,
KimLai2012_PRE,
HuLaiSeolEtAl2016_JCP,
Bartels,
Peng13,
RyKlYaCo16,
Sinha15,
Lowengrub13,
Hu,
Hu13}.
Conversely, the number of coarse-grained particles needed to track a GUV
in the HAP formalism is relatively large.  For microscopic process like
fusion, however, membrane deformations occur at a length scale
comparable to the thickness of the membrane
\cite{Kuzmin7235,Aeffner2012,KoKo2002}.  The small deformation
assumption of continuum theory no longer holds
\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The HAP theory
does encode membrane thickness through particle diameter, and it is
comparatively straightforward to account for proteins and lipid mixtures
by including several particle species.  Any ruptures or insertions occur
self-consistently in the HAP formulation.  Phase-field and level-set
methods also allow for topological changes but they require multiple
phase fields and level sets and additional (sometimes empirical) laws to
couple them to model membrane-membrane interactions
\cite{
DuLiuWang2004_JCP,
BibenKassnerMisbah2005_PRE,
DoyeuxGuyotChabannesEtAl2013_JCAM,
Du05,
QiangDu08,
doi:10.1098/rspa.2012.0505,
doi:10.1137/130941432,
Feetzl18,
doi:10.1137/16M1108406}.
In addition, these methods require the entire fluid and interfacial
domains to be discretized.  In contrast, the HAP methodology allows
evolution equations to be solved using integral equation methods that
when optimized have linear or near-linear computational complexity in
the number of particles~\cite{fmm1, fmm2, fmm3, fmm4, fmm5, fmm6, fmm7,
fmm8}.

>>>>

\section{Comments on structure of proposal}

\begin{itemize}
\item Background: should be much broader, example applications
\begin{itemize}
\item Vesicles for drug delivery
\item Extracellular vesicles (EVs) are newly recognized as important vectors for carrying and spreading antibiotic resistance genes (ARGs)
\item Building with nanoparticles, from the bottom up
\item Motivation:
MD and continuum simulations are clumsy; work over limited time/length scales; we need a
a robust method to complement established methods and processes.
The present proposal is our first attempt at creating such a model.
\end{itemize}

\item Model formulation: put the applied math formulas up front; change name ``particle'' to something else
\item Numerics: discuss advantages and challenges if BIE

\item Summary of respective resumes/contributions to this area

\item Specific Aim 1: Measuring material properties of amphiphile self-assembly
\item Specific Aim 2: Efficient, high-order methods for large-scale simulations
\item Specific Aim 3: Coarse graining and continuum models

\item Broader Impacts
\item Intellectual Merit
\item Prior NSF support

\item Other notes: do not waste the CV and prior work section:
play up significance of works.
``In our JFM/Nature/Biophys J paper'', ``In our much noticed,'' ``In our highly cited/referenced'', ``Detailed modeling and simulation which is the crown jewel of
applied mathematics''.
Use suggested reviewers to our advantage.

%Here is an interesting problem.
%Here is how it’s addressed.
%Here is what we are going to do.

\end{itemize}

@@

\section{Background}
\label{sec:background}

\textbf{Very broad introduction}

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[11]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.jpg}
 \caption{\label{fig:flow_map}
   In the HAP formulation,
   a system of exterior problems 
   defines the hydronamic and hydrophobic interactions.
   The colormap is for the intensity of $u$.
   The dynamics lead to self-organized structures like a vesicle bilayer.}
\end{wrapfigure}

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of 
partial differential equations (PDEs) that comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent. We then use a
second-order Adams-Bashforth method to update the particle configuration.
Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
particles and changes shape as the particles move.
Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. The free energy functional takes the form 
\begin{equation}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{equation}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
which is much smaller than characteristic time for 
particle motion \cite{MaGa13}.
Thus we assume $u$ minimizes $F[u]$ for all times.
Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
$u$ is bounded and satisfies the Euler-Lagrange equation
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle (Figure~\ref{fig:bcs}).

The particles lower the free energy $F[u]$ of the surrounding water
by moving. We calculate the rate of change of $F[u]$ using
\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
stress  
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques come from the integration of $\mathbf{T}$
along the particle boundary.
These forces and torques couple the Stokes equations \eqref{eq:stokes},
to semilinear elliptic equation \eqref{eq:SL}.
Solving for the translational and rotational velocities gives the
particle evolution.

\begin{wrapfigure}[10]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/3Particles.jpg}
 \caption{\label{fig:3particles}
   \footnotesize
   Particles translate and rotate to lower the free energy $F[u]$
   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
   The arrows are the velocity field $\mathbf{u}$.
 }
\end{wrapfigure}
The stress~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions (Figure \ref{fig:3particles}).

%By solving the above system, we obtain translational and angular
%velocities of the many-body system. A second-order Adams-Bashforth
%scheme updates the particle positions and orientations.

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step. The particle
boundaries are nearly touching and high-order numerical
schemes and adaptively chosen time-step sizes
are required to calculate trajectories accurately.
Furthermore, the domain is unbounded and care must be taken 
in capturing the far-field boundary conditions correctly. 
Finally, the numerical routine must handle large system sizes
efficiently.

%and
%\begin{equation}
%  \label{eq:force}
%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
%  \dif s = T_i, \qquad i=1,\ldots,N_b,
%\end{equation}
%where
%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
%particle outward normal.

\subsection{Boundary Integral formulation}
\textbf{Take from prior years proposal}

\subsection{Outline of the proposal}
